---
title: "Coffee_review"
output: html_document
date: "2023-12-16"
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(tidyr)
library(dplyr)
library(gcookbook)
library(stringr)
library(wordcloud)

knitr::opts_chunk$set(echo = TRUE)
```

### 1. Introduction
The purpose of this project is to visualize text data in coffee_review.csv, primarily in three columns: desc_1, desc_2, and desc_3. The visuals include the most common words, tf_idf, bigrams, and a world map showing the median price of coffee by region. 


```{r cars}
cr <- read.csv("coffee_review.csv")
glimpse(cr)
```
#### 1.1 Check the level of the variable roast
```{r }
cr$roast[cr$roast == '']<- 'Unspecified'
unique(cr$roast)
```
### 2. Text visuals
#### 2.1 The most common words  

```{r}
cr1_freq <- unnest_tokens(cr, word, desc_1) %>% 
  count(word, sort=TRUE)%>%
  filter(n>1150)%>%
  mutate(word = reorder(word, n))%>%
  anti_join(stop_words, by = join_by(word))%>% 
  ggplot(aes(n,word))+
  geom_col()+
  labs(x = "Frequency", y= " ")
cr1_freq
```


```{r, warning=FALSE}
cr2_freq <- unnest_tokens(cr, word, desc_2) %>% 
  count(word, sort=TRUE)%>%
  filter(n>1150)%>%
  mutate(word = reorder(word, n))%>%
  anti_join(stop_words, by = join_by(word))
 

ggplot(cr2_freq, aes(n,word))+
  geom_point()+
  geom_text(aes(label = n, check_overlap = FALSE), vjust=1.5, size = 4)+
  labs(x = "Frequency", y= " ")+ 
  theme(plot.title = element_text(hjust = 0.5, vjust = 3, size=16))
```

```{r}
cr3_freq <- unnest_tokens(cr, word, desc_3) %>% 
  count(word)%>%
  anti_join(stop_words,by = join_by(word))%>% 
  with(wordcloud(word,n, max.words = 100))

```

#### 2.2 Tf-idf
##### 2.2.1 Create a table with four columns: roast, word, n, and total
```{r}
cr1_words <- unnest_tokens(cr, word, desc_1) %>%
  count(roast, word, sort = TRUE)

cr2_words <- unnest_tokens(cr, word, desc_2) %>%
  count(roast,word, sort = TRUE)

cr3_words <- unnest_tokens(cr, word, desc_3) %>%
  count(roast,word, sort = TRUE)

```



```{r}
total_1 <- cr1_words %>% 
  summarize(total = sum(n))

cr1_words <- cross_join(cr1_words, total_1)

total_2 <- cr2_words %>% 
  summarize(total = sum(n))

cr2_words <- cross_join(cr2_words, total_2)

total_3 <- cr3_words %>% 
  summarize(total = sum(n))

cr3_words <- cross_join(cr3_words, total_3)

head(cr1_words)  
head(cr2_words)
head(cr3_words)

```

##### 2.2.2 Visualize term frequency by roast

```{r, warning = FALSE}
ggplot(cr1_words, aes(n/total, fill=roast)) +
  geom_histogram(show.legend = FALSE, bins = 30) +
  scale_fill_brewer(palette = "Set3")+
  xlim(NA, 0.0009) +
  facet_wrap(~roast, ncol = 2, scales = "free_y")

```


```{r, warning = FALSE}
ggplot(cr2_words, aes(n/total, fill=roast)) +
  geom_histogram(show.legend = FALSE, bins = 30) +
  scale_fill_brewer(palette = "Set3")+
  xlim(NA, 0.0009) +
  facet_wrap(~roast, ncol = 2, scales = "free_y")
```



```{r, warning = FALSE}
ggplot(cr3_words, aes(n/total, fill=roast)) +
  geom_histogram(show.legend = FALSE, bins = 30) +
  scale_fill_brewer(palette = "Set3")+
  xlim(NA, 0.0009) +
  facet_wrap(~roast, ncol = 2, scales = "free_y")
```

#### 2.2.3 bind_tf_idf() 

```{r}
cr1_tf_idf <- cr1_words%>%
  bind_tf_idf(word, roast, n)%>%
  arrange(desc(tf_idf))
head(cr1_tf_idf)
```

##### 2.2.4 Highest tf-idf words
```{r}
cr1_tf_idf %>%
  group_by(roast) %>%
  distinct(tf_idf, .keep_all=TRUE)%>%
  slice_max(tf_idf, n = 10) %>%
  ungroup() %>% 
  ggplot(aes(tf_idf,fct_reorder(word, tf_idf), fill = roast)) +
  scale_fill_brewer(palette = "Set3")+
  geom_col(show.legend = FALSE) +
  facet_wrap(~roast, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)+
  theme(text = element_text(size=8), plot.title = element_text(hjust = 0.5, vjust = 3))
```


#### 2.3 Bigrams 
##### 2.3.1 Create a table with bigrams and roast
```{r}
cr1_bigrams <- cr%>%
  unnest_tokens(bigram1, desc_1, token = "ngrams", n = 2) %>%
  filter(!is.na(bigram1))%>%
  select(roast, bigram1)

head(cr1_bigrams)  
```

```{r}
cr2_bigrams <- cr%>%
  unnest_tokens(bigram2, desc_2, token = "ngrams", n = 2) %>%
  filter(!is.na(bigram2))%>%
  select(roast, bigram2)

head(cr2_bigrams)
```

```{r}
cr3_bigrams <- cr%>%
  unnest_tokens(bigram3, desc_3, token = "ngrams", n = 2) %>%
  filter(!is.na(bigram3))%>%
  select(roast, bigram3) 

head(cr3_bigrams)
```


##### 2.3.2 Split  bigrams and remove cases where either word is a stop word
```{r}
cr1_separated <- cr1_bigrams%>%
  separate(bigram1, c("word1", "word2"), sep = " ")

cr1_filtered <- cr1_separated%>%
  filter(!word1%in% stop_words$word)%>%
  filter(!word2%in% stop_words$word)

cr1_counts <- cr1_filtered %>%
  count(word1,word2, sort=TRUE)

head(cr1_counts)
```



```{r}
cr2_separated <- cr2_bigrams%>%
  separate(bigram2, c("word1", "word2"), sep = " ")

cr2_filtered <- cr2_separated%>%
  filter(!word1%in% stop_words$word)%>%
  filter(!word2%in% stop_words$word)

cr2_counts <- cr2_filtered %>%
  count(word1,word2, sort=TRUE)

head(cr2_counts)
```



```{r}
cr3_separated <- cr3_bigrams%>%
  separate(bigram3, c("word1", "word2"), sep = " ")

cr3_filtered <- cr3_separated%>%
  filter(!word1%in% stop_words$word)%>%
  filter(!word2%in% stop_words$word)

cr3_counts <- cr3_filtered %>%
  count(word1,word2, sort=TRUE)

head(cr3_counts)
```


##### 2.3.3 Visualize bigrams
```{r}
cr1_united <- cr1_filtered %>%
  unite(bigram1, word1, word2, sep = " ")

cr1_tf_idf <- cr1_united %>%
  group_by(roast)%>%
  count(roast,bigram1) %>%
  bind_tf_idf(bigram1, roast, n) %>%
  arrange(desc(tf_idf))

head(cr1_tf_idf)
```


```{r}
cr1_tf_idf %>%
  group_by(roast) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(bigram1, tf_idf), fill = roast)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~roast, ncol = 2, scales = "free") +
  scale_fill_brewer(palette = "Set3")+
  labs(x = "tf-idf", y = NULL )+
  theme(text = element_text(size=8), plot.title = element_text(hjust = 0.5, vjust = 3))
```

```{r}
cr2_united <- cr2_filtered %>%
  unite(bigram2, word1, word2, sep = " ")

cr2_tf_idf <- cr2_united %>%
  group_by(roast)%>%
  count(roast,bigram2) %>%
  bind_tf_idf(bigram2, roast, n) %>%
  arrange(desc(tf_idf))

head(cr2_tf_idf)
```


```{r}
cr2_tf_idf %>%
  group_by(roast) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(bigram2, tf_idf), fill = roast)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~roast, ncol = 2, scales = "free") +
  scale_fill_brewer(palette = "Set3")+
  labs(x = "tf-idf", y = NULL )+
  theme(text = element_text(size=8), plot.title = element_text(hjust = 0.5, vjust = 3))
```


```{r}
cr3_united <- cr3_filtered %>%
  unite(bigram3, word1, word2, sep = " ")

cr3_tf_idf <- cr3_united %>%
  group_by(roast)%>%
  count(roast,bigram3) %>%
  bind_tf_idf(bigram3, roast, n) %>%
  arrange(desc(tf_idf))

head(cr3_tf_idf)
```


```{r}
cr3_tf_idf %>%
  group_by(roast) %>%
  slice_max(tf_idf, n = 10, with_ties = FALSE) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(bigram3, tf_idf), fill = roast)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~roast, ncol = 2, scales = "free") +
  scale_fill_brewer(palette = "Set3")+
  labs(x = "tf-idf", y = NULL )+
  theme(text = element_text(size=8), plot.title = element_text(hjust = 0.5, vjust = 3))
```


#### 2.4 Map region by the median coffee price

```{r}
world <- map_data("world")
worldplot <- ggplot() +
  geom_polygon(data = world, aes(x=long, y = lat, group = group)) + 
  coord_fixed(1.3)
```

##### 2.4.1 Rename selected regions 
```{r}
cr$loc_country [cr$loc_country == "United States And Floyd"]<-"United States"
cr$loc_country [cr$loc_country == "England"]<-"United Kingdom"
cr$loc_country [cr$loc_country == "New Taiwan"]<-"Taiwan"
cr$loc_country [cr$loc_country == "Hawai'i"]<-"Hawaii"
unique(cr$loc_country)
```

##### 2.4.2 Create cr_map by including loc_country and the median price of coffee by region
```{r}
cr_map <- cr%>%
  group_by(loc_country)%>%
  summarise_at(vars(X100g_USD), list(Price_usd= median))%>%
  select(region=loc_country, Price_usd)

```


##### 2.4.3  Check dataset differences and merge both datasets
```{r}
diff <- setdiff(world$region, cr_map$region)

worldSubset <- left_join(world, cr_map, by = "region")
head(worldSubset)
```


##### 2.4.4 Plot the final map to illustrate the median price of coffee by region

```{r}
plain <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank(),
  panel.background = element_rect(fill = "White"),
  plot.title = element_text(hjust = 0.5)
)

coffee_Price<- ggplot(data = worldSubset, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) +
  geom_polygon(aes(fill = Price_usd)) +
  scale_fill_distiller(palette ="YlOrBr", direction = -1) + 
  plain

coffee_Price
```

